---
pagetitle: "Regression Discontinuity: Figure with Points"
author: ""
date: ""
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Overview

```{r RDDPoints, fig.path = '../docs/figure/', warning = FALSE}
# Install and load packages ---------------
packages <- c(
  "tidyverse",
  "haven",
  "rdd",
  "splines"
)

# Change to install = TRUE to install the required packages
pacman::p_load(packages, character.only = TRUE, install = FALSE)

```

# Data

This graph comes from Gertler, Paul J.; Martinez, Sebastian; Premand, Patrick; Rawlings, Laura B.; Vermeersch, Christel M. J.. 2016. "Impact Evaluation in Practice, Second Edition" Washington, DC: Inter-American Development Bank and World Bank. 

https://openknowledge.worldbank.org/handle/10986/25030

- `household_identifier`: Household identifier
- `treatment_locality`: Timing variable (pre/post treatment)
- `eligible`: Identifier for households eligible for program of interest
- `round`: Timing (baseline or follow-up) identifier
- `health_expenditures`: Annualized out of pocket health expenditures

- Unit of Observation: Households

```{r RDDPoints, fig.path = '../docs/figure/', warning = FALSE}
# Load an example dataset ---------------
data <- read_dta("https://github.com/worldbank/r-econ-visual-library/raw/master/Library/Data/evaluation.dta")

# Printing the first five rows of the data to visualize its structure before data wrangling
head(data)

```

```{r RDDPoints, fig.path = '../docs/figure/', warning = FALSE}
# Data wrangling ---------------

# Set the cutoff level
cutoff <- 58

data <- data %>%
  filter(treatment_locality == 1) %>%
  mutate(treatment = (poverty_index <= cutoff))

# Printing the first five rows of the data to visualize its structure after data wrangling
head(data)

```

```{r RDDPoints, fig.path = '../docs/figure/', warning = FALSE}
# Create a graph ---------------

ggplot(data, aes(x = poverty_index, y = health_expenditures, color = treatment)) +
  geom_point(alpha = 0.2, size = 0.1) +
  geom_smooth(method = lm, formula = y ~ bs(x, 3), size = 1.0, se = FALSE) +
  geom_vline(xintercept = cutoff, linetype = "longdash") +
  ylim(c(0, 45)) +
  labs(
    x = "Baseline Poverty Index",
    y = "Health Expenditures ($)"
  ) +
  scale_color_brewer(palette = "Set2", labels = c("Not eligible", "Eligible")) +
  theme_classic() +
  theme(
    axis.text = element_text(size = 12),
    axis.title = element_text(size = 14),
    legend.title = element_blank(),
    legend.text = element_text(size = 11)
    )

```
