---
pagetitle: "Regression Coefficients: With graded error bars"
author: ""
date: ""
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Overview

Largely based on Figure 16.7 in [Fundamentals of Data Visualization](https://serialmentor.com/dataviz/visualizing-uncertainty.html).


```{r RegCoefGraded, fig.path = '../docs/figure/', warning = FALSE}
# Install and load packages ---------------
# devtools::install_github("wilkelab/ungeviz")
packages <- c(
  "tidyverse",
  "tidymodels",
  "ungeviz",
  "haven",
  "forcats",
  "colorspace",
  "grid",
  "caret",
  "lfe"
)

# Change to install = TRUE to install the required packages
pacman::p_load(packages, character.only = TRUE, install = FALSE)

```

# Data
This graph comes from David McKenzie, World Bank; Marcel Fafchamps, Stanford University; Simon Quinn, University of Oxford; Christopher Woodruff, University of Warwick. Ghana Microenterprise Growth and the Flypaper Effect, Randomized Experiment (MGFERE) 2008-2010. 

https://microdata.worldbank.org/index.php/catalog/2249

- `wave`: Survey wave identifier 
- `cashtreat`: assignment to the cash treatment
- `timetreat`: 
- `sheno`: Firm ID
- `control`: 

- Unit of Observation: Households

```{r RegCoefGraded, fig.path = '../docs/figure/', warning = FALSE}
# Load an example dataset ---------------
data <- read_dta("https://github.com/worldbank/r-econ-visual-library/raw/master/Library/Data/ReplicationDataGhanaJDE_short.dta")

# Printing the first five rows of the data to visualize its structure before data wrangling
head(data)

```

```{r RegCoefGraded, fig.path = '../docs/figure/', warning = FALSE}
# Data wrangling ---------------

# Treatment group includes only those who received in-kind treatment 
# between 2nd and 3rd waves, for simplicity
analysis_data <- data %>%
  filter(wave >= 2, cashtreat != 1) %>%
  group_by(sheno) %>%
  mutate(
    treatment = max((wave == 3) & (timetreat == 1)),
    control = all(control == 1),
    after = ifelse(wave >= 3, TRUE, FALSE),
    wave = relevel(as.factor(wave), ref = "2")
    ) %>%
  filter(treatment == TRUE | control == TRUE) %>%
  ungroup()

outcome_list <- c(
  "realfinalprofit", "expend_health_3months", 
  "expend_education_3months", "expend_total_3months"
  )

df_result <- tibble(y_var = outcome_list) %>%
  mutate(
    model_fe = map(
      # use felm to fit linear models with multiple group fixed effects
      y_var, ~ felm(as.formula(paste(.x, " ~ equiptreat * after | wave + sheno | 0 | sheno")), 
                    data = analysis_data)),
    tidied_model = map(model_fe, tidy)
  )

df_coef <- df_result %>%
  dplyr::select(y_var, tidied_model) %>%
  unnest(cols = tidied_model) %>%
  filter(term == "equiptreat:afterTRUE") %>%
  mutate(level_90 = 1, level_95 = 1) %>%
  pivot_longer(starts_with("level_"), names_to = "key", values_to = "levels") %>%
  mutate(
    levels = ifelse(key == "level_90", "90%", "95%"),
    lower_bound = ifelse(levels == "90%", 
                         estimate - 1.645 * std.error,
                         estimate - 1.96 * std.error),
    upper_bound = ifelse(levels == "90%",
                         estimate + 1.645 * std.error,
                         estimate + 1.96 * std.error)
    ) %>%
  mutate_if(is.double, round, digits = 2) 

# Printing the first five rows of the data to visualize its structure after data wrangling
head(df_coef)

```

```{r RegCoefGraded, fig.path = '../docs/figure/', warning = FALSE}
# Create a graph ---------------

ggplot(df_coef, aes(x = estimate, y = rev(y_var))) + 
  geom_errorbarh(
    aes(xmin = lower_bound, xmax = upper_bound, color = levels, size = levels),
    height = 0
  ) +
  geom_point(size = 2.5) +
  scale_x_continuous(limits = c(-30, 80)) +
  scale_color_manual(
    name = "Confidence level",
    values = c(
     `90%` = desaturate(darken("#0072B2", .2), .3),
     `95%` = desaturate(lighten("#0072B2", .4), .3)
    ),
    guide = guide_legend(
      direction = "horizontal",
      title.position = "top",
      label.position = "bottom"
    )
  ) +
  scale_size_manual(
    name = "Confidence level",
    values = c(
     `90%` = 2.,
     `95%` = 1.
    ),
    guide = guide_legend(
      direction = "horizontal",
      title.position = "top",
      label.position = "bottom"
    )
  ) +
  theme_classic() +
  geom_vline(xintercept = 0, size = 0.1, alpha = 0.5) +
  scale_y_discrete(labels = rev(c("3mo Real Profit (cedi)", "3mo Total Exp. (cedi)", 
                                  "3mo Health Exp. (cedi)",  "3mo Edu. Exp. (cedi)"))) +
  ylab("Point Estimates & 95% CI") +
  theme(
    axis.line = element_blank(),
    axis.text = element_text(size = 12),
    axis.title.y = element_text(size = 14),
    axis.title.x = element_blank(),
    axis.ticks.y = element_blank(),
    legend.position = c(1, 0.01),
    legend.justification = c(1, 0),
    legend.key.height = grid::unit(7, "pt"),
    legend.key.width = grid::unit(35, "pt"),
    legend.spacing.x = grid::unit(7, "pt"),
    legend.spacing.y = grid::unit(3.5, "pt"),
    legend.box.background = element_rect(fill = "white", color = NA),
    legend.box.spacing = grid::unit(0, "pt"),
    legend.title.align = 0.5
    )

```
