---
pagetitle: "Regression Coefficients: Point Estimates by Rounds"
author: ""
date: ""
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Overview


```{r RegCoefRounds, fig.path = '../docs/figure/', warning = FALSE}
# Install and load packages ---------------
packages <- c(
  "tidyverse",
  "haven",
  "forcats",
  "caret",
  "lfe"
)

# Change to install = TRUE to install the required packages
pacman::p_load(packages, character.only = TRUE, install = TRUE)
```

# Data

This graph comes from David McKenzie, World Bank; Marcel Fafchamps, Stanford University; Simon Quinn, University of Oxford; Christopher Woodruff, University of Warwick. Ghana Microenterprise Growth and the Flypaper Effect, Randomized Experiment (MGFERE) 2008-2010. 

https://microdata.worldbank.org/index.php/catalog/2249

- `sheno`: Firm ID
- `wave`: Survey wave identifier 
- `timetreat`: Treatment identifier 
- `control`: Timing (baseline or follow-up) identifier 
- `realfinalprofit`: Firm profit
- `cashtreat`: whether a respondent was given a cash treatment
- `equiptreat`: whether a respondent was given an equipment treatment

- Unit of Observation: Households

```{r RegCoefRounds, fig.path = '../docs/figure/', warning = FALSE}
# Load an example dataset ---------------

# Only relevant variables are kept in the dataset
data <- read_dta("https://github.com/worldbank/r-econ-visual-library/raw/master/Library/Data/ReplicationDataGhanaJDE_short.dta")

# Printing the first five rows of the data to visualize its structure before data wrangling
head(data)
```

```{r RegCoefRounds, fig.path = '../docs/figure/', warning = FALSE}
# Data wrangling ---------------

# Treatment group includes only those who received treatment 
# between 2nd and 3rd waves, for simplicity
analysis_data <- data %>%
  filter(wave >= 2) %>%
  group_by(sheno) %>%
  mutate(
    treatment = max((wave == 3) & (timetreat == 1)),
    control = all(control == 1),
    wave = relevel(as.factor(wave), ref = "2")
    ) %>%
  filter(treatment == TRUE | control == TRUE) %>%
  ungroup()

# Use felm to fit linear models with group fixed effects
res <- felm(
  realfinalprofit ~ (cashtreat + equiptreat) * wave | wave + sheno | 0 | sheno, 
  data = analysis_data
  )

var_list <- rownames(summary(res)$coef)
cash_var_list <- var_list[grepl("cashtreat:wave?", var_list)]
equip_var_list <- var_list[grepl("equiptreat:wave?", var_list)]

fig_data <- tibble(
  group = c(rep("Cash", length(cash_var_list)), rep("Equipment", length(equip_var_list))),
  wave = rep(paste0("Wave ", c("3", "4", "5", "6")), 2),
  coef = summary(res)$coef[c(cash_var_list, equip_var_list), "Estimate"],
  se = summary(res)$coef[c(cash_var_list, equip_var_list), "Cluster s.e."]
  )

# Printing the first five rows of the data to visualize its structure after data wrangling
head(fig_data)
```

```{r RegCoefRounds, fig.path = '../docs/figure/', warning = FALSE}
# Create a graph ---------------

ggplot(fig_data, aes(x = wave, y = coef, colour = group)) + 
  geom_pointrange(
    aes(ymin = coef - 1.96 * se, ymax = coef + 1.96 * se), 
    position = position_dodge(width = 0.9),
    alpha = 0.6, size = 0.5
    ) +
  geom_hline(yintercept = 0, size = 0.1, alpha = 0.5) +
  theme_classic() +
  ylab("Point Estimates & 95% CI") +
  scale_color_brewer(palette = "Set2", name = "Treatment Group") +
  theme(
    axis.line = element_blank(),
    axis.text = element_text(size = 12),
    axis.title.y = element_text(size = 15),
    axis.title.x = element_blank(),
    axis.ticks.y = element_blank(),
    legend.text = element_text(size = 12),
    legend.title = element_text(size = 14)
    )

```
