---
pagetitle: "Scatter Plots: Polynomial"
author: ""
date: ""
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Overview


```{r ScatterPolynomial, fig.path = '../docs/figure/', warning = FALSE}
# Install and load packages ---------------
packages <- c(
  "tidyverse",
  "haven",
  "latex2exp",
  "gridExtra",
  "lemon",
  "sciplot"
)

# Change to install = TRUE to install the required packages
pacman::p_load(packages, character.only = TRUE, install = FALSE)

```

# Data

This graph is based on Christian, Paul, and Brian Dillon. 2018. "Growing and Learning When Consumption Is Seasonal: Long-Term Evidence From Tanzania." Demography 55 (3): 1091–1118.
doi:10.1007/s13524-018-0669-4. 

The dataset used is a mock dataset based on the original paper's data. It contains data at the food type-month level. The relevant variables are:

- `cons_pae_m_sine`: M per AE (sine)
- `cons_pae_sd_sine`: standard deviation per AE (sine) 

- Unit of Observation:

```{r ScatterPolynomial, fig.path = '../docs/figure/', warning = FALSE}
# Load an example dataset ---------------
data <- read_dta("https://github.com/worldbank/r-econ-visual-library/raw/master/Library/Data/ScatterPolynomial.dta")

# Printing the first five rows of the data to visualize its structure before data wrangling
head(data)

```

```{r ScatterPolynomial, fig.path = '../docs/figure/', warning = FALSE}
# Data wrangling ---------------
subdata <- data %>%
  filter(cons_pae_m_sine < quantile(.$cons_pae_m_sine, 0.99) & cons_pae_m_sine > quantile(.$cons_pae_m_sine, 0.01))

# Printing the first five rows of the data to visualize its structure after data wrangling
head(subdata)

```

```{r ScatterPolynomial, fig.path = '../docs/figure/', message = FALSE, warning = FALSE}
# Create a graph ---------------

# Saving the ggplot object p1
p1 <- ggplot(subdata, aes(x = cons_pae_m_sine, y = cons_pae_sd_sine)) +
      geom_point(alpha = 0.2, size = 0.5) +
      geom_smooth(aes(colour = "red"), show.legend = TRUE) +
      theme_classic() +
      scale_colour_manual(name = "", values = "red", labels = "Local Poly. & 95% CI") +
      # Use TeX to allow for LaTeX expressions
      xlab(TeX("$\\widehat{m}$")) +
      ylab(TeX("$\\widehat{s}$"))

# Saving the ggplot object2
p2 <- ggplot(subdata, aes(x = cons_pae_m_sine, y = cv)) +
      geom_point(alpha = 0.2, size = 0.5) +
      geom_smooth(aes(colour = "red"), show.legend = TRUE) +
      theme_classic() +
      scale_colour_manual(name = "", values = "red", labels = "Local Poly. % 95% CI") +
      # Use TeX to allow for LaTeX characters 
      xlab(TeX("$\\widehat{m}$")) +
      ylab(TeX("$\\widehat{s} / \\widehat{m}$"))

# Use grid_arrange to display two plots
grid_arrange_shared_legend(p1, p2, position = "bottom")

```


