---
title: "Proportional Symbol Map"
author: ''
date: ''
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
```


```{r India_Energy_Analysis_Map, fig.path = '../docs/figure/'}
# Tested on R Version 4.2.2
# sf Version 1.0.21
# dplyr Version 1.1.4
# tmap Version 4.1
# pacman Version 0.5.1
# readr Version 2.1.5
# rnaturalearth Version 1.0.1
# rnaturalearthdata Version 1.0.0
# tidyr Version 1.3.1

# Install and load packages -------------
packages <- c("sf", 
              "dplyr", 
              "tmap", 
              "pacman", 
              "readr", 
              "rnaturalearth",
              "rnaturalearthdata", 
              "tidyr")

# Change to install = TRUE to install the required packages
pacman::p_load(packages, character.only = TRUE, install = TRUE)

# Load the Ember Energy dataset -------------------
ember_data_raw <- read_csv("/Users/koniks/Downloads/india_yearly_full_release_long_format.csv") #replace path with url to .csv from GitHub
india_states <- ne_states(country = "India", returnclass = "sf")

energy_data_2022 <- ember_data_raw %>%
  filter(Year == 2022) %>%
  filter(
    (Category == "Electricity generation" & Subcategory == "Aggregate fuel" & Variable %in% c("Clean", "Fossil", "Renewables") & Unit == "%") |
    (Category == "Electricity generation" & Subcategory == "Total" & Variable == "Total Generation" & Unit == "GWh") |
    (Category == "Capacity" & Subcategory == "Aggregate fuel" & Variable %in% c("Clean", "Fossil", "Renewables") & Unit == "MW") |
    (Category == "Power sector emissions" & Subcategory == "CO2 intensity" & Variable == "CO2 intensity" & Unit == "gCO2/kWh")
  ) %>%
  mutate(
    metric_name = case_when(
      Category == "Electricity generation" & Variable == "Clean" ~ "clean_generation_pct",
      Category == "Electricity generation" & Variable == "Fossil" ~ "fossil_generation_pct", 
      Category == "Electricity generation" & Variable == "Renewables" ~ "renewable_generation_pct",
      Category == "Electricity generation" & Variable == "Total Generation" ~ "total_generation_gwh",
      Category == "Capacity" & Variable == "Clean" ~ "clean_capacity_mw",
      Category == "Capacity" & Variable == "Fossil" ~ "fossil_capacity_mw",
      Category == "Capacity" & Variable == "Renewables" ~ "renewable_capacity_mw",
      Category == "Power sector emissions" & Variable == "CO2 intensity" ~ "co2_intensity_gco2_kwh",
      TRUE ~ paste(Category, Variable, sep = "_")
    )
  ) %>%
  select(State, metric_name, Value) %>%
  pivot_wider(names_from = metric_name, values_from = Value) %>%
  filter(!if_all(-State, is.na))

# Create categories for proportional symbol representation ---------------
energy_analysis <- energy_data_2022 %>%
  mutate(
    # Clean energy performance categories
    clean_performance = case_when(
      clean_generation_pct >= 80 ~ "Excellent Clean Energy (80%+)",
      clean_generation_pct >= 60 ~ "Good Clean Energy (60-79%)",
      clean_generation_pct >= 40 ~ "Moderate Clean Energy (40-59%)",
      clean_generation_pct >= 20 ~ "Low Clean Energy (20-39%)",
      TRUE ~ "Minimal Clean Energy (<20%)"
    ),
    # Total generation size categories  
    generation_size = case_when(
      total_generation_gwh >= 50000 ~ "Very Large (50+ TWh)",
      total_generation_gwh >= 20000 ~ "Large (20-50 TWh)",
      total_generation_gwh >= 5000 ~ "Medium (5-20 TWh)",
      total_generation_gwh >= 1000 ~ "Small (1-5 TWh)",
      TRUE ~ "Very Small (<1 TWh)"
    ),
    # CO2 intensity categories
    co2_category = case_when(
      co2_intensity_gco2_kwh <= 300 ~ "Low Carbon (≤300g)",
      co2_intensity_gco2_kwh <= 600 ~ "Medium Carbon (300-600g)",
      co2_intensity_gco2_kwh <= 900 ~ "High Carbon (600-900g)",
      TRUE ~ "Very High Carbon (>900g)"
    ),
    # Overall energy score (weighted combination)
    energy_score = (clean_generation_pct * 0.5) + 
                   (pmax(0, 100 - (co2_intensity_gco2_kwh/10)) * 0.3) +
                   (pmin(100, (total_generation_gwh/1000)) * 0.2),
    
    energy_grade = case_when(
      energy_score >= 80 ~ "A+ Excellent",
      energy_score >= 70 ~ "A Good", 
      energy_score >= 60 ~ "B+ Above Average",
      energy_score >= 50 ~ "B Average",
      energy_score >= 40 ~ "C Below Average",
      TRUE ~ "D Poor"
    )
  ) %>%
  mutate(
    # Create factors for proper ordering
    clean_performance = factor(clean_performance, 
                             levels = c("Minimal Clean Energy (<20%)", "Low Clean Energy (20-39%)",
                                      "Moderate Clean Energy (40-59%)", "Good Clean Energy (60-79%)",
                                      "Excellent Clean Energy (80%+)")),
    generation_size = factor(generation_size,
                           levels = c("Very Small (<1 TWh)", "Small (1-5 TWh)", "Medium (5-20 TWh)",
                                    "Large (20-50 TWh)", "Very Large (50+ TWh)")),
    energy_grade = factor(energy_grade,
                        levels = c("D Poor", "C Below Average", "B Average", "B+ Above Average", "A Good", "A+ Excellent"))
  )

# Clean state names for joining ---------------------
india_states_clean <- india_states %>%
  mutate(
    state_clean = case_when(
      name == "Dadra and Nagar Haveli and Daman and Diu" ~ "Dadra and Nagar Haveli",
      name == "Jammu and Kashmir" ~ "Jammu and Kashmir",
      name == "Telangana" ~ "Telangana", 
      name == "Chhattisgarh" ~ "Chhattisgarh",
      TRUE ~ name
    )
  )

# Join energy data to spatial data ---------------------
india_energy_map <- india_states_clean %>%
  left_join(energy_analysis, by = c("state_clean" = "State")) %>%
  filter(!is.na(clean_generation_pct))

# Create color palettes -------------------------
clean_colors <- c(
  "Minimal Clean Energy (<20%)" = "#d73027",     # Red
  "Low Clean Energy (20-39%)" = "#fc8d59",       # Orange
  "Moderate Clean Energy (40-59%)" = "#fee08b",  # Yellow
  "Good Clean Energy (60-79%)" = "#91bfdb",      # Light blue  
  "Excellent Clean Energy (80%+)" = "#4575b4"    # Dark blue
)

grade_colors <- c(
  "D Poor" = "#d73027",
  "C Below Average" = "#f46d43", 
  "B Average" = "#fdae61",
  "B+ Above Average" = "#abd9e9",
  "A Good" = "#74add1",
  "A+ Excellent" = "#313695"
)
```


```{r plotting}
# Create multiple visualizations ------------------------------------
tmap_mode("plot")

# Map 1: Clean Energy Performance with Generation Size symbols
map1 <- tm_shape(india_energy_map) +
  tm_polygons(
    col = "clean_performance",
    palette = clean_colors,
    border.col = "black",
    border.lwd = 0.5,
    title = "Clean Energy Performance",
    legend.show = TRUE
  ) +
  tm_symbols(
    size = "total_generation_gwh",
    scale = 2,
    col = "generation_size",
    palette = c("#ffffcc", "#c7e9b4", "#7fcdbb", "#41b6c4", "#225ea8"),
    border.col = "white",
    border.lwd = 1,
    title.size = "Total Generation (GWh)",
    title.col = "Generation Scale",
    alpha = 0.8,
    shape = 21
  ) +
  tm_credits("Source: Ember Energy India Data 2022", 
             position = c("right", "bottom"), size = 0.6)

# Map 2: Overall Energy Grade with CO2 Intensity
map2 <- tm_shape(india_energy_map) +
  tm_polygons(
    col = "energy_grade",
    palette = "white",
    border.col = "#91bfdb",
    border.lwd = 0.5,
    title = "Overall Energy Grade",
    legend.show = TRUE
  ) +
  tm_symbols(
    size = "co2_intensity_gco2_kwh",
    scale = 1.5,
    col = "co2_category", 
    palette = c("#1a9850", "#91bfdb", "#fc8d59", "#d73027"),
    border.col = "white",
    border.lwd = 1,
    title.size = "CO2 Intensity (g/kWh)",
    title.col = "Carbon Intensity",
    alpha = 0.8,
    shape = 21
  ) +
  tm_credits("Source: Ember Energy India Data 2022", 
             position = c("right", "bottom"), size = 0.6)

# Display both maps
print("=== CLEAN ENERGY PERFORMANCE MAP ===")
map1

print("=== OVERALL ENERGY GRADE MAP ===") 
map2
```

## Instructions for Using Real Data

To use real electricity access data instead of the sample data above:

### Option 1: Ember Energy Data
```r
# Download data from: https://ember-energy.org/data/india-electricity-data/
# Load the CSV file and process it
real_data <- read_csv("path/to/ember_india_data.csv") %>%
  filter(year == 2022) %>%  # or latest available year
  select(state = State, electricity_access = AccessRate)
```

### Option 2: Central Electricity Authority
```r
# Download from: https://cea.nic.in/dashboard/
# Process the Excel/CSV files they provide
```

### Option 3: Data For India
```r
# Use their API or download CSV from: 
# https://www.dataforindia.com/access-to-electricity/
```

### Alternative Shapefile Sources
If you want more detailed/accurate boundaries:
- **GADM**: Uncomment the GADM section in the code above
- **Survey of India**: Official boundaries (requires registration)
- **GitHub repositories**: Several open-source options available
